Adaptive broadcast tree for multicores

### 2013-08-06 measurements/ziger_topologies.tex
Adding missing experiments

\begin{table}[htb]
  \centering
  \begin{tabular}{lrrrrr}
  \toprule
  & \multicolumn{3}{c}{Real hardware} & \multicolumn{2}{c}{Simulation} \\
  topology & time [cycles] & factor & stderr & time [units] & factor \\
  \midrule
  cluster & 2634.91 & 1.017 & 48.11 & 334 & 1.100 \\
  mst & 3178.59 & 1.227 & 43.28 & 343 & 1.129 \\
  bintree & 3380.46 & 1.305 & 42.70 & 377 & 1.242 \\
  sequential & 3841.91 & 1.483 & 239.48 & 672 & 2.214 \\
  badtree & 5711.52 & 2.204 & 30.49 & 714 & 2.354 \\
  adaptivetree & 2591.14 & \colorbox{gray}{1.000} & 45.12 & 303 & \colorbox{gray}{1.000} \\
  \midrule
  \end{tabular}
  \caption{Evaluation of different topologies for ziger}
  \label{tab:ziger}
\end{table}

>>>>

\begin{table}[htb]
  \centering
  \begin{tabular}{lrrrrr}
  \toprule
  & \multicolumn{3}{c}{Real hardware [cycles]} & \multicolumn{2}{c}{Simulation [units]} \\
  topology & time & factor & stderr & time & factor \\
  \midrule
  cluster & 2634.91 & 1.017 & 48.11 & 334 & 1.100 \\
  mst & 3178.59 & 1.227 & 43.28 & 343 & 1.129 \\
  bintree & 3380.46 & 1.305 & 42.70 & 377 & 1.242 \\
  sequential & 3841.91 & 1.483 & 239.48 & 672 & 2.214 \\
  badtree & 5711.52 & 2.204 & 30.49 & 714 & 2.354 \\
  adaptivetree & 2591.14 & \colorbox{gray}{1.000} & 45.12 & 303 & \colorbox{gray}{1.000} \\
  \midrule
  \end{tabular}
  \caption{Topology evaluation for \ziger}
  \label{tab:ziger}
\end{table}
